%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Abstract}

Simulation of human soft tissues in contact with their environment
is essential in many fields, including visual effects and apparel
design.  Biological tissues are nearly incompressible. However,
standard methods employ compressible elasticity models and achieve
incompressibility indirectly by setting Poisson's ratio to be close
to 0.5.  This approach can produce results that are plausible
qualitatively but inaccurate quantatively. This approach also causes
numerical instabilities and locking in coarse discretizations or
otherwise pose a prohibitive restriction on the size of the time
step.
%
We propose a novel approach to alleviate these issues by
replacing indirect volume preservation using Poisson's ratios with
direct enforcement of zonal volume constraints, while controlling
fine-scale volumetric deformation through a cell-wise penalty.
To increase realism, we propose an epidermis model to mimic the
dramatically higher surface stiffness on real skinned bodies.
We demonstrate that our method produces stable realistic
deformations with precise volume preservation but without locking
artifacts. 
Due to the volume preservation not being tied to mesh discretization, our method also allows a
resolution consistent simulation of incompressible materials.
Our method improves the stability of the standard
Neo-Hookean model and the general compression recovery in the Stable
Neo-Hookean model.

% Consider placing version information if you circulate multiple drafts
%\vfill
%\begin{center}
%\begin{sf}
%\fbox{Revision: \today}
%\end{sf}
%\end{center}
